---
title: "Exhaustive Searches"
output: html_document
date: "2023-10-14"
---

```{r}
library(readxl)
concrete = read_excel("Concrete_Data.xls")
new_names = c("cement", "furnace_slag", "fly_ash", "water", "superplasticizer",
              "coarse_agg", "fine_agg", "age", "concrete_strength")
colnames(concrete) = new_names
```

Given that the total number of possible predictors is 7 (), an exhaustive search of the full set of possible models is viable.

```{r}
library(leaps) 
exh = regsubsets(concrete_strength ~.-water, data = concrete, nvmax = 8) 
exhs = summary(exh)
exhs$outmat
```
From this search, it can be found that cement is the best predictor for concrete compressive strength for a model of size 1. 
To find the best model, the coefficient of determination (R-Squared) will be plotted against the models of each size.

```{r}
plot(exh, scale = "r2")
```

The highest R-Squared value is found in a model of full size (0.61), which agrees with the findings of the Backward variable selection model.

