---
title: "Initial Assumption Checking"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    number_sections: true
date: "2023-10-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Cleaning

```{r message=FALSE}
# Import the required packages.
library(readxl)
library(tidyverse)
library(broom)
library(cowplot)
```

```{r}
concrete = read_excel("Concrete_Data.xls")

# rename the variables
# store old names
old_names = colnames(concrete)

# create new names on the order of the old names
new_names = c("cement", "furnace_slag", "fly_ash", "water", "superplasticizer",
              "coarse_agg", "fine_agg", "age", "concrete_strength")

# overwrite old names with new names
colnames(concrete) = new_names
```

# Post Model-Selection Slope-Significance Test

## Introduction

After the performance assessment, we found that the model created by backward stepwise scheme and exhaustive search scheme perform better than the model created by forward stepwise scheme. Hence, the model created by backward stepwise scheme is our selected model. 

We are going to perform Slope-significance test on the selected model to see whether each of the variables in the model has significance enough slope to have linear relationship with the dependent variable to fulfil the linear relationship assumption of linear regression model.

## Test

```{r}
data = subset(concrete, select = -c(water))
M1 = lm(data$concrete_strength ~ ., data = data)
M1 |> broom::tidy()
```

## Conclusion

All the variables in the model have small p-value. Hence, there is strong evidence that suggest all the variables have linear relationship with the dependent variable.

