---
title: "Residual&normality&homo.Rmd"
author: "Congying Yang"
date: "2023-10-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#residual and normality
```{r}
library(ggfortify)
library(ggplot2)
concrete <- read_excel("~/Downloads/concrete+compressive+strength/Concrete_Data.xls")
new_names = c("cement", "furnace_slag", "fly_ash", "water", "superplasticizer",
              "coarse_agg", "fine_agg", "age", "concrete_strength")
colnames(concrete) = new_names
lm1 = lm(concrete_strength ~ cement + superplasticizer + age + furnace_slag + fly_ash, concrete)
autoplot(lm1, which = 1:2) + theme_bw()
```


Linearity: There's linear relationship in this model due to the unsymemetrically distributed above and below zero in residual plot

Homoskedasticity: The residual vs fitted plot shows the varience is consistent which indicates that this model is homoskedasticity and the assumption of homogeneous varience is valid.

Normality: The QQ plot shows a straight line which indicates that the normality assumption is reasonable without outlier. 



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
