---
title: "Project Presentation Title"
subtitle: "Group 001A01"
author: "Person 1, Person 2, Person 3, Person 4 and Person 5"
format: 
  revealjs:
    auto-slide: 20000
    embed-resources: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Slide title

I am a slide with a **plot**

```{r, echo=FALSE, message=FALSE, fig.height=6, fig.width=10}
library(ggplot2)
ggplot(mtcars) +
  aes(x = mpg) + 
  geom_histogram() + 
  theme_classic(base_size = 22)
```





## Slide title {.larger}

I am a slide with a *table*

```{r, message = FALSE, echo = FALSE}
library(gt)
library(dplyr)
mtcars |> group_by(cyl) |> 
  summarise(mean_mpg = mean(mpg),
            sd_mpg = sd(mpg),
            mean_wt = mean(wt),
            sd_wt = sd(wt)) |> 
  gt::gt() |>  
  gt::fmt_number(columns = 2:5, decimals = 1) |> 
  gt::cols_label(cyl = "Number of cylinders",
                 mean_mpg = "Mean",
                 sd_mpg = "SD",
                 mean_wt = "Mean",
                 sd_wt = "SD") |> 
  gt::tab_spanner(columns = ends_with("_mpg"),"Miles per gallon")|> 
  gt::tab_spanner(columns = ends_with("_wt"),"Weight (1000 lbs)")
```




## Slide title

I am slide three content with maths

$$E = mc^2$$



## Slide title

Content



## Slide title

Content



## Slide title

Content




## Slide title

Content




## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Slide title

Content



## Last slide

This is slide 20. You can't have more than 20 slides (including the title slide)!
